Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2021-08-17 RR_manuscript/Draft_RR.Rmd
:recycle: - rephrase introduction to highlight

These researcher degrees of freedom are both a blessing and a curse.
They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis [e.g., @box1976science; @tukey1977exploratory; @de2014thought].
They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted [@simmons2011false].
Recent projects have shown that the variability between different data analysts is vast and can lead independent researchers to draw different conclusions from the same data set [e.g., @silberzahn2018many; @starns2019assessing; @botvinik2020variability].
These studies, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to how already obtained numbers are statistically analyzed.
Those numbers are usually the result of a complex measurement process that translates human behavior into numbers.
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
This is not trivial, given the temporal extension of the acoustic signal and its complex structural composition.
Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.

In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the operationalization of a complex signal and decisions regarding the statistical analysis.
<!-- TODOLATER: include number of teams when known -->
Specifically, we discuss the impact of analytic decision making on research results obtained by N teams who had access to the same set of acoustic recordings in order to answer the same research question. 
Our goals are twofold: First, our study conceptually replicates previous many-analyses projects, probing previously observed flexibility in statistical analyses in order to independently confirm previously published findings and probe its generalizability to other disciplines (here speech sciences). 
Second, our study extends previous findings and estimates the amount of observed flexibility in quantifying complex human behavior (here human speech). 
This is important because previous studies might have investigated only the lower bound of variability across analysts because analysts did not have to quantify the variables under investigation but were instead already provided with numerical data.

>>>>

These researcher degrees of freedom are both a blessing and a curse.
They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypotheses [e.g., @box1976science; @tukey1977exploratory; @de2014thought].
They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted [@simmons2011false].
Recent projects have shown that the variability between different data analysts is vast and can lead independent researchers to draw different conclusions from the same data set [e.g., @silberzahn2018many; @starns2019assessing; @botvinik2020variability].
These studies, however, might still underestimate the extent to which analysts vary because data analysis is not restricted to the statistical analysis of ready-made numeric data.
These data can in fact be the result of complex measurement processes that translate a phenomenon, such as human behavior, into numbers.
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it, in other words, how to operationalise the phenomenon under study.
This is not trivial, given the temporal extension of the acoustic signal and its complex structural composition.
<!-- Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself. -->

In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the *operationalization* of a complex signal and decisions regarding *statistical analysis*.
<!-- TODOLATER: include number of teams when known -->
Specifically, we discuss the degree of variability in research results obtained by N teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same same set of speech recordings.
Our goals are twofold: First, our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences).
Second, our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices", deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed.
